### 2016-12-13 manuscript/reviews/response.Rmd

#### Comment
Fig 7: as beautiful as this is, you should label the sidebar as "logit" or "centered logit" instead of "y".
#### Response
Fixed. Color key labeled "Average logit".

### Suggestions for the software

#### Comment
I understand that you like the feature of having a one-shot function partial to both generate and plot the PDP. I realize that the default is `FALS`E. However, I still think it's a disservice to the user as constructing PDP's is computationally intense and if they get the plot wrong or it's not to their liking, they will have to regenerate the whole thing again. So, it is my opinion that you should take it out and force two steps: generation and illustration.
#### Response
While I am not suggesting that the `partial` function needs to mimic the behavior of the PDP fucntions in `randomForest` and `gbm`, I do find it useful to be able to plot the results without forcing the user to store them. However, I agree with your concern which is why `partial` has `plot = FALSE` as the default. Furthermore, I have made it possible to retrieve the raw PDP data even when \code{plot = TRUE}. This is because the "trellis" object returned by `partial` \ `plotPartial` now contains an additional `partial.data` attribute. This is described in the package documentation. For example,
```{r, eval=TRUE}
library(pdp)
data(trees)
mod <- lm(Volume ~ ., data = trees)
partial(mod, pred.var = "Girth", plot = TRUE)
pdp.Girth <- lattice::trellis.last.object()
pd.Girth <- attr(pdp.Girth, "partial.data")
head(pd.Girth)
```

#### Comment
The package could be more powerful if you allowed a predict function as a parameter. For instance, you cannot currently use random forests to illustrate classification probabilities.
#### Response
I agree, and I have changed the behavior of `...` to refer to additional parameters to `stats::predict` (e.g., the `n.trees` argument in `predict.gbm`.). However, I'm not sure yet about the scale on which the predictions are plotted. For now, I am more comfortable leaving as the usual logit scale defined for PDPs (mostly so that they are defined the same whatever the number of class outcomes). But I am not opposed to making this (simple) change in the future. I have added this as a feature request: https://github.com/bgreenwell/pdp/issues/21.

### 2016-12-15 README.Rmd
tweaks based on review comments

In this example, we fit a random forest to the Boston housing data. (See `?boston` for a brief explanation of the data.) Note, for any of the following examples, you can see a progress bar by simply specifying `progress = "text"` in the call to `partial`. You may also reduce the computation time via the `grid.resolution` option in the call to `partial`.
```{r, message = FALSE, warning=FALSE, fig.show="hold"}
# Load required packages
library(pdp)  # for constructing PDPs
library(randomForest)  # for random forest algorithm

@@

# Partial dependence of lstat and rm on cmedv
partial(boston.rf, pred.var = "lstat", plot = TRUE, rug = TRUE)
partial(boston.rf, pred.var = "rm", plot = TRUE, rug = TRUE)
partial(boston.rf, pred.var = c("lstat", "rm"), plot = TRUE, chull = TRUE)
```

@@

# Partial dependence of glucose and age on diabetes test result (neg/pos). 
partial(pima.svm, pred.var = c("glucose", "age"), plot = TRUE, chull = TRUE)
```

@@

For illustration we use `caret`'s `train` function to tune an [XGBoost](https://github.com/dmlc/xgboost) model to the Pima Indians diabetes data using 5-fold cross-validation. We then use the final model to construct PDPs for `glucose` and `age`. Note, when training a model using `caret`'s `train` function, you can view tuning progress by setting `verboseIter = TRUE` in the call to `trainControl`.
```{r, message=FALSE, warning=FALSE}
# Load required packages
library(caret)  # for model training/tuning

@@

# Partial dependence of glucose and age on diabetes test result (neg/pos)
partial(pima.xgb, pred.var = "glucose", plot = TRUE, rug = TRUE)
partial(pima.xgb, pred.var = "age", plot = TRUE, rug = TRUE)
partial(pima.xgb, pred.var = "mass", plot = TRUE, chull = TRUE)
```

>>>>

In this example, we fit a random forest to the Boston housing data. (See `?boston` for a brief explanation of the data.) Note, for any of the following examples, you can see a progress bar by simply specifying `progress = "text"` in the call to `partial`. You may also reduce the computation time via the `grid.resolution` option in the call to `partial`.
```{r, message = FALSE, warning=FALSE, fig.width=12, fig.height=4}
# Load required packages
library(pdp)  # for constructing PDPs
library(randomForest)  # for random forest algorithm

@@

# Partial dependence of lstat and rm on cmedv
grid.arrange(
  partial(boston.rf, pred.var = "lstat", plot = TRUE, rug = TRUE),
  partial(boston.rf, pred.var = "rm", plot = TRUE, rug = TRUE),
  partial(boston.rf, pred.var = c("lstat", "rm"), plot = TRUE, chull = TRUE),
  ncol = 3
)

```

@@

# Partial dependence of glucose and age on diabetes test result (neg/pos). 
partial(pima.svm, pred.var = c("glucose", "age"), plot = TRUE, chull = TRUE,
        train = pima)
```

@@

For illustration we use `caret`'s `train` function to tune an [XGBoost](https://github.com/dmlc/xgboost) model to the Pima Indians diabetes data using 5-fold cross-validation. We then use the final model to construct PDPs for `glucose` and `age`. Note, when training a model using `caret`'s `train` function, you can view tuning progress by setting `verboseIter = TRUE` in the call to `trainControl`.
```{r, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
# Load required packages
library(caret)  # for model training/tuning

@@

# Partial dependence of glucose and age on diabetes test result (neg/pos)
grid.arrange(
  partial(pima.xgb, pred.var = "glucose", plot = TRUE, rug = TRUE),
  partial(pima.xgb, pred.var = "age", plot = TRUE, rug = TRUE),
  partial(pima.xgb, pred.var = "mass", plot = TRUE, rug = TRUE),
  ncol = 3 
)
```
